Experience-Biased Symbolic Planning

### 2014-05-12 AAAI_AuthorKit/paper.tex
References section

Suppose we have a consistent heuristic $h(S,S')$ for the distance between arbitrary pairs of states.
That is, $h$ obeys the triangle inequality with respect to edge costs, and $h(S,S) = 0$ for all $S\in V$.
The E-graph heuristic $h^E$ biases the search to follow E-Graph edges instead of $h$ by penalizing the latter by an inflation factor $\epsilon^E > 1$.
To be precise, define

@@

\textit{For sufficiently large $\epsilon^E$, once the A* frontier touches an E-graph component which includes a goal state, no node outside the E-graph will ever again need to be expanded.} This means, for instance, that if the E-graph already contains a path from the start to a goal, then A* guided by $h^E$ with large bias term $\epsilon^E$ will never leave the E-graph. If the E-graph is small, a solution would promptly be discovered.

@@

In a preprocessing stage before the main search, we apply Dijkstra's algorithm once in reverse with the costs $c'$ to compute the estimated distance-to-goal $h^E(S)$ from every $S\in V^E$. If the blackbox heuristic $h$ is cheap to compute, this preprocessing takes $O(|V^E|^2)$ time, which is negligible for small E-graphs.

@@

The above figure illustrates the idea. Suppose the dark edges have cost 3 and make up the E-graph. Non-E-graph edges are not shown; instead, light edges represent the jump estimates $h(S_i,S_j) = 2$ (with one exception: $h(S,G) = 5$), which we inflate by a factor $\epsilon^E=2$ to make 4 (or 10, respectively). Dijkstra's algorithm follows the edges backward to compute the $h^E$ values shown alongside each node.

$G$ is on the E-graph, though this need not be the case in general. $V^E$ is the pentagon on the right, and its $h^E$ values are precomputed before the search. $h^E(S)$ is computed only when A* generates $S\notin V^E$.

@@

\bibliographystyle{aaai}
\bibliography{paper.bib}

>>>>

Suppose we have a consistent heuristic $h(S,S')$ for the distance between arbitrary pairs of states.
That is, $h$ obeys the triangle inequality, is never dominated by an edge cost, and $h(S,S) = 0$ for all $S\in V$.
The E-graph heuristic $h^E$ biases the search to follow E-Graph edges instead of $h$ by penalizing the latter by an inflation factor $\epsilon^E > 1$.
To be precise, define

@@

\textit{For sufficiently large $\epsilon^E$, once the A* frontier touches an E-graph component which includes a goal state, no node outside the E-graph will ever again need to be expanded.} This means, for instance, that if the E-graph already contains a path from the start to a goal, then A*, guided by $h^E$ with large bias parameter $\epsilon^E$, will never leave the E-graph. If the E-graph is small, a solution would promptly be discovered.

@@

In a preprocessing stage before the main search, we apply Dijkstra's algorithm once in reverse with the costs $c'$ to compute the estimated distance-to-goal $h^E(S)$ from every $S\in V^E$. If the heuristic $h$ is cheap to compute, this preprocessing takes $O(|V^E|^2)$ time, which is insignificant for small E-graphs and goal sets.

@@

The above figure illustrates the idea. Suppose the dark edges have cost 3 and make up the E-graph. Off-E-graph edges are not shown, as they are only accessed indirectly via $h$; instead, light edges represent the jump estimates $h(S_i,S_j) = 2$ (with one exception: $h(S,G) = 5$), which we inflate by a factor $\epsilon^E=2$ to make 4 (or 10, respectively). Dijkstra's algorithm follows dark and light edges backward to compute the $h^E$ values shown alongside each node.

$G$ is on the E-graph, though this need not be the case in general. $V^E$ is the pentagon on the right, and its $h^E$ values are precomputed before the search. For $S\notin V^E$, $h^E(S)$ is computed only when A* generates $S$.

@@

\bibliographystyle{aaai}
\bibliography{paper}
